title: "DC rbokeh"
author: "Radovan Kavicky"
date: "18 March 2018"
output: html_notebook

data2: https://data.worldbank.org/data-catalog/world-development-indicators
data: https://data.worldbank.org/data-catalog
---
###Data from [World bank](https://data.worldbank.org/data-catalog/world-development-indicators), after download, also unzip into "your Working directory/data" and choose/import "WDIData.csv". 
#### - First, we will load the .csv (nearly 200 MB/it will take a while) 
```{r, echo=TRUE, message=FALSE, warning = FALSE}
library(readr)
library(dplyr)
dat <- read_csv("data/WDIData.csv")
```
## Data
#### - Check the imported data 
```{r, echo=TRUE, message=FALSE, warning = FALSE}
dat
```
## Data (different view)
#### - Check the data structure (via dplyr's Glimpse function).
```{r, echo=TRUE, message=FALSE, warning = FALSE}
glimpse(dat)
```
## Let's filter & tidy this mess
#### - Select one (GDP growth from 60's till 2016) indicator for UK, USA and EU + Make checking data via Glimpse great again!
```{r}
library(tidyr)
dc <- dat %>% 
filter(`Indicator Name`=="GDP growth (annual %)") %>%
filter(`Country Name`==c("United Kingdom", "United States", "European Union"))
glimpse(dc)
```
## Still not tidy enough!
#### - Let's tidy some more (select only what we need & transform from wide to long dataset & NA's out).
#### - & Take a Glimpse again.
```{r}
names(dc) 
dc1 <- select(dc, "Country Name", "Indicator Name", 5:61)
dc2 <- gather(dc1, key="Year", value="GDP growth (annual %)", -"Country Name", na.rm=TRUE) 
glimpse(dc2)
```
## Still not a tidy dataset!
#### - Let's remove first 3 rows (no data there).
#### - & Glimpse again.
```{r}
dc2
dc2 <- dc2[-c(1:3), ]
dc2
dc2$Year <- as.numeric(dc2$Year)
dc2$`GDP growth (annual %)` <- as.numeric(dc2$`GDP growth (annual %)`)
class(dc2$Year)
class(dc2$`GDP growth (annual %)`)
glimpse(dc2)
```
## Tidy enough & We can start plotting now!
#### - Let's import rbokeh and make it a line plot by a country.
```{r, echo=TRUE, message=FALSE, warning = FALSE}
library(rbokeh)
p <- figure(width = 600, height = 350, legend_location = "top_right", title = "GDP Growth (%) USA, EU, UK", logo = NULL) %>%
  ly_lines(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, width = 5, col = "Country Name")
p
```
## Congratulations, your first plot! But still not publication quality... let's customize some more...
#### - We will add points too.
#### - Put it black and transparent (using alpha transparency)
```{r, echo=TRUE, message=FALSE, warning = FALSE}
library(rbokeh)
q <- figure(width = 600, height = 350, legend_location = "top_right", title = "GDP Growth (%) USA, EU, UK", logo = NULL) %>%
  ly_lines(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, width = 5, col = "Country Name") %>%
ly_points(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, size = 4, col = "black") 
q
```
## Not bad! But still not publication quality... what about the legend? (it is covering our points)
```{r, echo=TRUE, message=FALSE, warning = FALSE}
library(rbokeh)
r <- figure(width = 600, height = 350, legend_location = "top_right", title = "GDP Growth (%) USA, EU, UK", logo = NULL) %>%
  ly_lines(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, width = 5, col = "Country Name") %>%
ly_points(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, size = 4, col = "black") %>%
theme_legend(border_line_width = 1, background_fill_alpha = 0.1, label_text_font_size = "8pt", label_text_align = "left", label_text_font = "Garamond", label_text_font_style = "bold") 
r
```
## Getting better! But still not publication quality... what about the title? 
```{r, echo=TRUE, message=FALSE, warning = FALSE}
library(rbokeh)
s <- figure(width = 600, height = 350, legend_location = "top_right", title = "GDP Growth (%) USA, EU, UK", logo = NULL) %>%
  ly_lines(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, width = 5, col = "Country Name") %>%
ly_points(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, size = 4, col = "black") %>%
theme_legend(border_line_width = 1, background_fill_alpha = 0.1, label_text_font_size = "8pt", label_text_align = "left", label_text_font = "Garamond", label_text_font_style = "bold") %>%
theme_title(text_align = "center", text_font = "Garamond", text_font_size = "14pt", text_baseline = "bottom") 
s
```
## Definitely better! But still not publication quality... what about the axis? 
#### - Let's make it bold & Garamond too (Pipe it via theme_axis).
```{r, echo=TRUE, message=FALSE, warning = FALSE}
library(rbokeh)
t <- figure(width = 600, height = 350, legend_location = "top_right", title = "GDP Growth (%) USA, EU, UK", logo = NULL) %>%
  ly_lines(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, width = 5, col = "Country Name") %>%
ly_points(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, size = 4, col = "black") %>%
theme_legend(border_line_width = 1, background_fill_alpha = 0.1, label_text_font_size = "8pt", label_text_align = "left", label_text_font = "Garamond", label_text_font_style = "bold") %>%
theme_title(text_align = "center", text_font = "Garamond", text_font_size = "14pt", text_baseline = "bottom") %>%
theme_axis(axis_label_text_font = "Garamond",
axis_label_text_font_size = "12pt", axis_label_text_font_style = "bold", major_label_text_font = "Garamond", major_label_text_font_size = "10pt",
major_label_text_font_style = "bold") 
t
```
## Nearly there! But still not publication quality... it is growth, right? What about to make it visually distinctive (divide positive/negative growth)? 
#### - rbokeh allows us to do this via ly_abline, so let's Pipe it there ([a,b] to [0,0]).
```{r, echo=TRUE, message=FALSE, warning = FALSE}
library(rbokeh)
library(htmlwidgets)
u <- figure(width = 600, height = 350, legend_location = "top_right", title = "GDP Growth (%) USA, EU, UK", logo = NULL, tools = c("pan", "wheel_zoom", "box_zoom", "box_select", "reset", "resize")) %>%
  ly_lines(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, width = 5, col = "Country Name") %>%
ly_points(x="Year", y="GDP growth (annual %)", data = dc2,
    alpha = 0.5, size = 4, col = "black") %>%
theme_legend(border_line_width = 1, background_fill_alpha = 0.1, label_text_font_size = "8pt", label_text_align = "left", label_text_font = "Garamond", label_text_font_style = "bold") %>%
theme_title(text_align = "center", text_font = "Garamond", text_font_size = "14pt", text_baseline = "bottom") %>%
theme_axis(axis_label_text_font = "Garamond",
axis_label_text_font_size = "12pt", axis_label_text_font_style = "bold", major_label_text_font = "Garamond", major_label_text_font_size = "10pt",
major_label_text_font_style = "bold") %>%
ly_abline(a = 0, b = 0, v = NULL, h = NULL, coef = NULL,
color = "black", width = 1, type = 1, legend = NULL,
visible = TRUE) %>%
tool_lasso_select()
u
saveWidget(u, file="rbokeh001.html")
```
##Congratulations! You have now the publication quality figure ready for you & it's all interactive!