---
title: "TidyWeek Week1"
output: html_document
---

# 1. Participants (Name of the Student & Mentor)

```{r setup, include=FALSE}
#load your packages here and set your code options here.
knitr::opts_chunk$set(echo = TRUE)
```

# 2. Background information & Objectives of your analysis

* What sort of information does someone else reading this need to know? 
* What is the objective of your analysis? (What is your driving question?)
* What sort of steps or structure will your analysis follow?


# 3. Data

* What is included in this data? 
* What isn't included? 
* Where did it come from?
* Who collected it and how?
* What tools were used?
```{r data}
#load in your data here!
```


# 4. Tidying Data

* What did you notice that was obvious about your data that needed to be fixed?
* What steps will you take?
* What to do about missing/incomplete data?

# 5. Analysis

* What is your approach to answer your question?
* What methods are you using?
* What are your assumptions and how are they justified?
* How can someone learn more about the techniques used?
* Why did you choose the visualizations that you did?

# 6. Conclusions

* What was the answer to your question?  Why?  
* Is your conclusion valid?  Under what circumstances?
* Is there anything else that might better explain your conclusion?
* What did you learn from this exercise?
* How would you approach a problem like this next time?

# External resources
* [github repo](https://github.com/you/your-repo)
* [link to yout website](https://mywebsite.com)